\item \underline{Zach Cutler}, Jack Wilburn, Hilson Shrestha, Yiren Ding, Brian Bollen, \underline{Khandaker Abrar Nadib}, Tingying He, Andrew McNutt, Lane Harrison, \textbf{Alexander Lex}. ReVISit 2: A Full Experiment Life Cycle User Study Framework. IEEE Transactions on Visualization and Computer Graphics (VIS), vol.\ 32, 2026. \textbf{IEEE VIS 2025 Best Paper Award}
\item \underline{Haihan Lin}, \underline{Maxim Lisnic}, Derya Akbaba, Miriah Meyer, \textbf{Alexander Lex}. Here’s what you need to know about my data: Exploring Expert Knowledge’s Role in Data Analysis. IEEE Transactions on Visualization and Computer Graphics (VIS), vol.\ 32, no.\ 1, \doi{10.1109/TVCG.2025.3634821}, 2026. \textbf{IEEE VIS 2025 Honorable Mention Award}
\item Tingying He, Maggie McCracken, Daniel Hajas, Sarah Creem-Regehr, \textbf{Alexander Lex}. Using Tactile Charts to Support Comprehension and Learning of Complex Visualizations for Blind and Low-Vision Individuals. IEEE Transactions on Visualization and Computer Graphics (VIS), vol.\ 32, 2026. 
\item Sehi L’Yi, Harrison G. Zhang, Andrew P. Mar, Thomas C. Smits, Lawrence Weru, Sofía Rojas, \textbf{Alexander Lex}, Nils Gehlenborg. A Comprehensive Evaluation of Life Sciences Data Resources Reveals Significant Accessibility Barriers. Scientific Reports, vol.\ 15, no.\ 1, pp.\ 23676, \doi{10.1038/s41598-025-08731-7}, 2025. 
\item Andrew McNutt, Maggie K McCracken, Ishrat Jahan Eliza, Daniel Hajas, Jake Wagoner, Nate Lanza, Jack Wilburn, Sarah Creem-Regehr, \textbf{Alexander Lex}. Accessible Text Descriptions for UpSet Plots. Computer Graphics Forum (EuroVis), vol.\ 44, no.\ 3, \doi{10.1111/cgf.70102}, 2025. 
\item \underline{Maxim Lisnic}, \underline{Zach Cutler}, Marina Kogan, \textbf{Alexander Lex}. Visualization Guardrails: Designing Interventions Against Cherry-Picking in Interactive Data Explorers. ACM SIGCHI Conference on Human Factors in Computing Systems (CHI), pp.\ 1-19, \doi{10.1145/3706598.3713385}, 2025. 
\item \underline{Zach Cutler}, Lane Harrison, \underline{Carolina Nobre}, \textbf{Alexander Lex}. Crowdsourced Think-Aloud Studies. ACM SIGCHI Conference on Human Factors in Computing Systems (CHI), pp.\ 1-23, \doi{10.1145/3706598.3714305}, 2025. 
\item \underline{Devin Lange}, Robert Judson-Torres, Thomas A. Zangle, \textbf{Alexander Lex}. Aardvark: Composite Visualizations of Trees, Time-Series, and Images. IEEE Transactions on Visualization and Computer Graphics (VIS), vol.\ 31, no.\ 1, pp.\ 1290–1300, \doi{10.1109/TVCG.2024.3456193}, 2024. \textbf{IEEE VIS 2024 Best Paper Award}
\item Klaus Eckelt, \underline{Kiran Gadhave}, \textbf{Alexander Lex}, Marc Streit. Loops: Leveraging Provenance and Visualization to Support Exploratory Data Analysis in Notebooks. IEEE Transactions on Visualization and Computer Graphics (VIS), vol.\ 31, no.\ 1, pp.\ 1213–1223, \doi{10.31219/osf.io/79eyn}, 2024. 
\item \underline{Maxim Lisnic}, \textbf{Alexander Lex}, Marina Kogan. ‘Yeah, this graph doesn't show that’: Analysis of Online Engagement with Misleading Data Visualizations. ACM SIGCHI Conference on Human Factors in Computing Systems (CHI), pp.\ 1-14, \doi{10.1145/3613904.3642448}, 2024. 
\item \underline{Kiran Gadhave}, \underline{Zach Cutler}, \textbf{Alexander Lex}. Persist: Persistent and Reusable Interactions in Computational Notebooks. Computer Graphics Forum (EuroVis), vol.\ 43, no.\ 3, \doi{10.1111/cgf.15092}, 2024. 
\item Yiren Ding, Jack Wilburn, Hilson Shrestha, Akim Ndlovu, \underline{Kiran Gadhave}, \underline{Carolina Nobre}, \textbf{Alexander Lex}, Lane Harrison. reVISit: Supporting Scalable Evaluation of Interactive Visualizations. IEEE IEEE Visualization and Visual Analytics (VIS), pp.\ 31-35, \doi{10.1109/VIS54172.2023.00015}, 2023. 
\item \underline{Devin Lange}, \underline{Shaurya Sahai}, Jeff M. Phillips, \textbf{Alexander Lex}. Ferret: Reviewing Tabular Datasets for Manipulation. Computer Graphics Forum (EuroVis), vol.\ 42, no.\ 3, pp.\ 187-198, \doi{10.1111/cgf.14822}, 2023. 
\item \underline{Maxim Lisnic}, Cole Polychronis, \textbf{Alexander Lex}, Marina Kogan. Misleading Beyond Visual Tricks: How People Actually Lie with Charts. ACM SIGCHI Conference on Human Factors in Computing Systems (CHI), pp.\ 1-21, \doi{10.1145/3544548.3580910}, 2023. 
\item Derya Akbaba, \underline{Devin Lange}, Michael Correll, \textbf{Alexander Lex}, Miriah Meyer. Troubling Collaboration: Matters of Care for Visualization Design Study. ACM SIGCHI Conference on Human Factors in Computing Systems (CHI), pp.\ 1-15, \doi{10.1145/3544548.3581168}, 2023. 
\item \underline{Haihan Lin}, Derya Akbaba, Miriah Meyer, \textbf{Alexander Lex}. Data Hunches: Incorporating Personal Knowledge into Visualizations. , vol.\ 29, no.\ 1, pp.\ 504-514, \doi{10.1109/TVCG.2022.3209451}, 2022. 
\item \underline{Kiran Gadhave}, \underline{Zach Cutler}, \textbf{Alexander Lex}. Reusing Interactive Analysis Workflows. Computer Graphics Forum (EuroVis), vol.\ 41, no.\ 3, pp.\ 133–144, \doi{10.1111/cgf.14528}, 2022. 
\item \underline{Devin Lange}, Eddie Polanco, Robert Judson-Torres, Thomas A. Zangle, \textbf{Alexander Lex}. Loon: Using Exemplars to Visualize Large-Scale Microscopy Data. IEEE Transactions on Visualization and Computer Graphics (VIS), vol.\ 28, no.\ 1, pp.\ 248-258, \doi{10.1109/TVCG.2021.3114766}, 2021. \textbf{IEEE VIS 2021 Honorable Mention Award}
\item \underline{Kiran Gadhave}, Jochen Görtler, \underline{Zach Cutler}, \underline{Carolina Nobre}, Oliver Deussen, Miriah Meyer, Jeff Phillips, \textbf{Alexander Lex}. Predicting Intent Behind Selections in Scatterplot Visualizations. Information Visualization, vol.\ 20, no.\ 4, pp.\ 207–228, \doi{10.1177/14738716211038604}, 2021. 
\item \underline{Jen Rogers}, Austin H Patton, Luke Harmon, \textbf{Alexander Lex}, Miriah Meyer. Insights From Experiments With Rigor in an EvoBio Design Study. IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 27, no.\ 2, pp.\ 1106-1116, \doi{10.1109/TVCG.2020.3030405}, 2021. 
\item \underline{Haihan Lin}, Ryan A. Metcalf, Jack Wilburn, \textbf{Alexander Lex}. Sanguine: Visual Analysis for Patient Blood Management. Information Visualization, vol.\ 20, no.\ 2-3, pp.\ 123-137, \doi{10.1177/14738716211028565}, 2021. 
\item \underline{Carolina Nobre}, \underline{Dylan Wootton}, \underline{Zach Cutler}, Lane Harrison, Hanspeter Pfister, \textbf{Alexander Lex}. reVISit: Looking Under the Hood of Interactive Visualization Studies. ACM SIGCHI Conference on Human Factors in Computing Systems (CHI), pp.\ 1-13, \doi{10.1145/3411764.3445382}, 2021. 
\item \underline{Haihan Lin}, Ryan A. Metcalf, Jack Wilburn, \textbf{Alexander Lex}. Sanguine: Visual Analysis for Patient Blood Management.  Workshop on Visual Analytics in Healthcare at AMIA (VAHC), 2020. 
\item \underline{Zach Cutler}, \underline{Kiran Gadhave}, \textbf{Alexander Lex}. Trrack: A Library for Provenance-Tracking in Web-Based Visualizations.  IEEE Visualization Conference (VIS), pp.\ 116-120, \doi{10.1109/VIS47514.2020.00030}, 2020. 
\item \underline{Carolina Nobre}, \underline{Dylan Wootton}, Lane Harrison, \textbf{Alexander Lex}. Evaluating Multivariate Network Visualization Techniques Using a Validated Design and Crowdsourcing Approach. ACM SIGCHI Conference on Human Factors in Computing Systems (CHI), pp.\ 1-12, \doi{10.1145/3313831.3376381}, 2020. 
\item Katarina Furmanova, Samuel Gratzl, Holger Stitz, Thomas Zichner, Miroslava Jaresova, \textbf{Alexander Lex}, Marc Streit. Taggle: Scalable Visualization of Tabular Data through Aggregation. Information Visualization, vol.\ 19, no.\ 2, pp.\ 114-136, \doi{10.1177/1473871619878085}, 2019. 
\item Alex Bigelow, \underline{Carolina Nobre}, Miriah Meyer, \textbf{Alexander Lex}. Origraph: Interactive Network Wrangling.  IEEE Conference on Visual Analytics Science and Technology (VAST), pp.\ 81-92, \doi{10.1109/VAST47406.2019.8986909}, 2019. 
\item G. Elisabeta Marai, Bruno Pinaud, Katja Bühler, \textbf{Alexander Lex}, John H. Morris. Ten Simple Rules to Create Biological Network Figures for Communication. PLOS Computational Biology, vol.\ 15, no.\ 9, pp.\ e1007244, \doi{10.1371/journal.pcbi.1007244}, 2019. 
\item \underline{Carolina Nobre}, Marc Streit, Miriah Meyer, \textbf{Alexander Lex}. The State of the Art in Visualizing Multivariate Networks. Computer Graphics Forum (EuroVis), vol.\ 38, pp.\ 807-832, \doi{10.1111/cgf.13728}, 2019. 
\item \underline{Jen Rogers}, Nicholas Spina, Ashley Neese, Rachel Hess, Darrel Brodke, \textbf{Alexander Lex}. Composer: Visual Cohort Analysis of Patient Outcomes. Applied Clinical Informatics, vol.\ 10, no.\ 2, pp.\ 278-285, \doi{10.1055/s-0039-1687862}, 2019. 
\item \underline{Carolina Nobre}, Marc Streit, \textbf{Alexander Lex}. Juniper: A Tree+Table Approach to Multivariate Graph Visualization. IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 25, no.\ 1, pp.\ 544-554, \doi{10.1109/TVCG.2018.2865149}, 2019. 
\item \underline{Carolina Nobre}, Nils Gehlenborg, Hilary Coon, \textbf{Alexander Lex}. Lineage: Visualizing Multivariate Clinical Data in Genealogy Graphs. IEEE Transactions on Visualization and Computer Graphics, vol.\ 25, no.\ 3, pp.\ 1543-1558, \doi{10.1109/TVCG.2018.2811488}, 2019. 
\item Yan Zheng, Yi Ou, \textbf{Alexander Lex}, Jeff M. Phillips. Visualization of Big Spatial Data using Coresets for Kernel Density Estimates. IEEE Transactions on Big Data, vol.\ 7, no.\ 3, pp.\ 524-534, \doi{10.1109/TBDATA.2019.2913655}, 2019. 
\item \underline{Jen Rogers}, Nicholas Spina, Ashley Neese, Rachel Hess, Darrel Brodke, \textbf{Alexander Lex}. Composer: Visual Cohort Analysis of Patient Outcomes.  Workshop on Visual Analytics in Healthcare at AMIA (VAHC 2018), 2018. 
\item Yan Zheng, Yi Ou, \textbf{Alexander Lex}, Jeff M. Phillips. Visualization of Big Spatial Data using Coresets for Kernel Density Estimates. IEEE IEEE Symposium on Visualization in Data Science (VDS), \doi{10.1109/VDS.2017.8573446}, 2017. 
\item Jake R. Conway, \textbf{Alexander Lex}, Nils Gehlenborg. UpSetR: An R Package For The Visualization Of Intersecting Sets And Their Properties. Bioinformatics, vol.\ 33, no.\ 18, pp.\ 2938-2940, \doi{10.1093/bioinformatics/btx364}, 2017. 
\item \underline{Michael Kern}, \textbf{Alexander Lex}, Nils Gehlenborg, Chris R. Johnson. Interactive Visual Exploration And Refinement Of Cluster Assignments. BMC Bioinformatics, vol.\ 18, no.\ 1, pp.\ 406, \doi{10.1186/s12859-017-1813-7}, 2017. 
\item Ethan Kerzner, \textbf{Alexander Lex}, Crystal Lynn Sigulinsky, Timothy Urness, Bryan William Jones, Robert E. Marc, Miriah Meyer. Graffinity: Visualizing Connectivity In Large Graphs. Computer Graphics Forum (EuroVis), vol.\ 36, no.\ 3, pp.\ 251-260, \doi{10.1111/cgf.13184}, 2017. 
\item Thomas Geymayer, Manuela Waldner, \textbf{Alexander Lex}, Dieter Schmalstieg. How Sensemaking Tools Influence Display Space Usage. The Eurographics Association EuroVis Workshop on Visual Analytics (EuroVA), \doi{10.2312/eurova.20171112}, 2017. 
\item Sean McKenna, \textbf{Alexander Lex}, Miriah Meyer. Worksheets for Guiding Novices through the Visualization Design Process. IEEE IEEE Workshop on Pedagogy of Data Visualization (PDV), 2017. 
\item Hendrik Strobelt, Bilal Alsallakh, Joseph Botors, Brant Peterson, Mark Borowsky, Hanspeter Pfister, \textbf{Alexander Lex}. Vials: Visualizing Alternative Splicing of Genes. IEEE Transactions on Visualization and Computer Graphics (InfoVis ’15), vol.\ 22, no.\ 1, pp.\ 399--408, \doi{10.1109/TVCG.2015.2467911}, 2016. 
\item Christian Partl, Samuel Gratzl, Marc Streit, Anne Mai Wassermann, Hanspeter Pfister, Dieter Schmalstieg, \textbf{Alexander Lex}. Pathfinder: Visual Analysis of Paths in Graphs. Computer Graphics Forum (EuroVis), vol.\ 35, no.\ 3, pp.\ 71--80, \doi{10.1111/cgf.12883}, 2016. \textbf{EuroVis 2016 Honorable Mention Award}
\item Samuel Gratzl, \textbf{Alexander Lex}, Nils Gehlenborg, Nicola Cosgrove, Marc Streit. From Visual Exploration to Storytelling and Back Again. Computer Graphics Forum (EuroVis), vol.\ 35, no.\ 3, pp.\ 491--500, \doi{10.1111/cgf.12925}, 2016. 
\item \underline{Carolina Nobre}, \textbf{Alexander Lex}. OceanPaths: Visualizing Multivariate Oceanography Data. The Eurographics Association Proceedings of the Eurographics Conference on Visualization (EuroVis ’15) - Short Papers, \doi{10.2312/eurovisshort.20151124}, 2015. 
\item Christian Partl, \textbf{Alexander Lex}, Hendrik Strobelt, Anne Mai Wassermann, Hanspeter Pfister, Dieter Schmalstieg. ConTour: Data-Driven Exploration of Multi-Relational Datasets for Drug Discovery. IEEE Transactions on Visualization and Computer Graphics (VAST), vol.\ 20, no.\ 12, pp.\ 1883--1892, \doi{10.1109/TVCG.2014.2346752}, 2014. 
\item Marc Streit, \textbf{Alexander Lex}, Samuel Gratzl, Christian Partl, Dieter Schmalstieg, Hanspeter Pfister, Peter Park, Nils Gehlenborg. Guided Visual Exploration of Genomic Stratifications in Cancer. Nature Methods, vol.\ 11, no.\ 9, pp.\ 884--885, \doi{10.1038/nmeth.3088}, 2014. 
\item Thomas Geymayer, Markus Steinberger, \textbf{Alexander Lex}, Marc Streit, Dieter Schmalstieg. Show me the Invisible: Visualizing Hidden Content. ACM Press Proceedings of the SIGCHI Conference on Human Factors in Computing Systems (CHI ’14), pp.\ 3705--3714, \doi{10.1145/2556288.2557032}, 2014. \textbf{ACM CHI 2014 Honorable Mention Award}
\item Samuel Gratzl, Nils Gehlenborg, \textbf{Alexander Lex}, Hanspeter Pfister, Marc Streit. Domino: Extracting, Comparing, and Manipulating Subsets across Multiple Tabular Datasets . IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 20, no.\ 12, pp.\ 2023--2032, \doi{10.1109/TVCG.2014.2346260}, 2014. \textbf{IEEE InfoVis 2014 Honorable Mention Award}
\item Johnathan D Mercer, Balaji Pandian, \textbf{Alexander Lex}, Nicolas Bonnel, Hanspeter Pfister. Mu-8: Visualizing Differences between Proteins and their Families . BMC Proceedings, vol.\ 8, no.\ Suppl 2, pp.\ S5, \doi{10.1186/1753-6561-8-S2-S5}, 2014. 
\item \textbf{Alexander Lex}, Nils Gehlenborg, Hendrik Strobelt, Romain Vuillemot, Hanspeter Pfister. UpSet: Visualization of Intersecting Sets. IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 20, no.\ 12, pp.\ 1983--1992, \doi{10.1109/TVCG.2014.2346248}, 2014. \textbf{10 Year InfoVis Test of Time Award, 2024}
\item Cagatay Turkay, \textbf{Alexander Lex}, Marc Streit, Hanspeter Pfister, Helwig Hauser. Characterizing Cancer Subtypes using the Dual Analysis Approach in Caleydo StratomeX. IEEE Computer Graphics and Applications, vol.\ 34, no.\ 2, pp.\ 38--47, \doi{10.1109/MCG.2014.1}, 2014. 
\item \textbf{Alexander Lex}, Christian Partl, Denis Kalkofen, Marc Streit, Anne Mai Wassermann, Samuel Gratzl, Dieter Schmalstieg, Hanspeter Pfister. Entourage: Visualizing Relationships between Biological Pathways using Contextual Subsets. IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 19, no.\ 12, pp.\ 2536--2545, \doi{10.1109/TVCG.2013.154}, 2013. 
\item Samuel Gratzl, \textbf{Alexander Lex}, Nils Gehlenborg, Hanspeter Pfister, Marc Streit. LineUp: Visual Analysis of Multi-Attribute Rankings. IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 19, no.\ 12, pp.\ 2277--2286, \doi{10.1109/TVCG.2013.173}, 2013. \textbf{IEEE InfoVis 2013 Best Paper Award}
\item Christian Partl, \textbf{Alexander Lex}, Marc Streit, Denis Kalkofen, Karl Kashofer, Dieter Schmalstieg. enRoute: Dynamic Path Extraction from Biological Pathway Maps for Exploring Heterogeneous Experimental Datasets. BMC Bioinformatics, vol.\ 14, no.\ Suppl 19, pp.\ S3, \doi{10.1186/1471-2105-14-S19-S3}, 2013. 
\item Christian Partl, \textbf{Alexander Lex}, Marc Streit, Denis Kalkofen, Karl Kashofer, Dieter Schmalstieg. enRoute: Dynamic Path Extraction from Biological Pathway Maps for In-Depth Experimental Data Analysis.  Proceedings of the IEEE Symposium on Biological Data Visualization (BioVis ’12), pp.\ 107--114, \doi{10.1109/BioVis.2012.6378600}, 2012. \textbf{IEEE BioVis 2012 Best Paper Award}
\item Marc Streit, Hans-Jörg Schulz, \textbf{Alexander Lex}, Dieter Schmalstieg, Heidrun Schumann. Model-Driven Design for the Visual Analysis of Heterogeneous Data . IEEE Transactions on Visualization and Computer Graphics, vol.\ 18, no.\ 6, pp.\ 998--1010, \doi{10.1109/TVCG.2011.108}, 2012. 
\item \textbf{Alexander Lex}, Marc Streit, Hans-Jörg Schulz, Christian Partl, Dieter Schmalstieg, Peter Park, Nils Gehlenborg. StratomeX: Visual Analysis of Large-Scale Heterogeneous Genomics Data for Cancer Subtype Characterization. Computer Graphics Forum (EuroVis), vol.\ 31, no.\ 3, pp.\ 1175--1184, \doi{10.1111/j.1467-8659.2012.03110.x}, 2012. \textbf{EuroVis 2012 3rd Best Paper Award}
\item Clemens Holzhüter, \textbf{Alexander Lex}, Dieter Schmalstieg, Hans-Jörg Schulz, Heidrun Schumann, Marc Streit. Visualizing Uncertainty in Biological Expression Data.  Proceedings of the SPIE Conference on Visualization and Data Analysis (VDA), vol.\ 8294, pp.\ 82940O-82940O-11, \doi{10.1117/12.908516}, 2012. 
\item \textbf{Alexander Lex}, Hans-Jörg Schulz, Marc Streit, Christian Partl, Dieter Schmalstieg. VisBricks: Multiform Visualization of Large, Inhomogeneous Data . IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 17, no.\ 12, pp.\ 2291--2300, \doi{10.1109/TVCG.2011.250}, 2011. 
\item Markus Steinberger, Manuela Waldner, Marc Streit, \textbf{Alexander Lex}, Dieter Schmalstieg. Context-Preserving Visual Links. IEEE Transactions on Visualization and Computer Graphics (InfoVis'11), vol.\ 17, no.\ 12, pp.\ 2249--2258, \doi{10.1109/TVCG.2011.183}, 2011. \textbf{IEEE InfoVis 2011 Best Paper Award}
\item Thomas Geymayer, \textbf{Alexander Lex}, Marc Streit, Dieter Schmalstieg. Visualizing the Effects of Logically Combined Filters. IEEE Computer Society Press Proceedings of the Conference on Information Visualisation (IV), pp.\ 47–52, \doi{10.1109/IV.2011.52}, 2011. 
\item \textbf{Alexander Lex}, Marc Streit, Ernst Kruijff, Dieter Schmalstieg. Caleydo: Design and Evaluation of a Visual Analysis Framework for Gene Expression Data in its Biological Context.  Proceedings of IEEE Pacific Visualization Symposium (PacificVis), pp.\ 57--64, \doi{10.1109/PACIFICVIS.2010.5429609}, 2010. 
\item \textbf{Alexander Lex}, Marc Streit, Christian Partl, Karl Kashofer, Dieter Schmalstieg. Comparative Analysis of Multidimensional, Quantitative Data . IEEE Transactions on Visualization and Computer Graphics (InfoVis), vol.\ 16, no.\ 6, pp.\ 1027--1035, \doi{10.1109/TVCG.2010.138}, 2010. 
\item Manuela Waldner, Werner Puff, \textbf{Alexander Lex}, Marc Streit, Dieter Schmalstieg. Visual Links across Applications. Canadian Human-Computer Communications Society Proceedings of the Graphics Interface (GI), pp.\ 129--136, 2010. \textbf{GI 2010 Best Student Paper Award}
\item Manuela Waldner, \textbf{Alexander Lex}, Marc Streit, Dieter Schmalstieg. Design Considerations for Collaborative Information Workspaces in Multi-Display Environments.  Proceedings of Workshop on Collaborative Visualization on Interactive Surfaces (CoVIS'09, VisWeek), pp.\ 36--39, 2009. 
\item Marc Streit, \textbf{Alexander Lex}, Heimo Müller, Dieter Schmalstieg. Gaze-Based Focus Adaption in an Information Visualization System.  Proceedings of the Conference on Computer Graphics and Visualization and Image Processing (CGVCVIP), 2009. 
\item Marc Streit, \textbf{Alexander Lex}, Michael Kalkusch, Kurt Zatloukal, Dieter Schmalstieg. Caleydo: Connecting Pathways with Gene Expression . Bioinformatics, vol.\ 25, no.\ 20, pp.\ 2760--2761, \doi{10.1093/bioinformatics/btp432}, 2009. 
\item Heimo Müller, Robert Reihs, Stefan Sauer, Kurt Zatloukal, Marc Streit, \textbf{Alexander Lex}, Bernhard Schlegl, Dieter Schmalstieg. Connecting Genes with Diseases.  Proceedings of the Conference on Information Visualisation (IV ’09), pp.\ 323--330, \doi{10.1109/IV.2009.86}, 2009. 
