\item Yiren Ding, Jack Wilburn, Hilson Shrestha, Akim Ndlovu, \uline{Kiran Gadhave}, \uline{Carolina Nobre}, \textbf{Alexander Lex}, Lane Harrison. \textit{reVISit: Supporting Scalable Evaluation of Interactive Visualizations}. IEEE IEEE Visualization and Visual Analytics (VIS), pp.\ 31-35, \doi{10.1109/VIS54172.2023.00015}, 2023. 
\item \uline{Haihan Lin}, Ryan A. Metcalf, Jack Wilburn, \textbf{Alexander Lex}. \textit{Sanguine: Visual Analysis for Patient Blood Management}.  Workshop on Visual Analytics in Healthcare at AMIA (VAHC), 2020. 
\item \uline{Zach Cutler}, \uline{Kiran Gadhave}, \textbf{Alexander Lex}. \textit{Trrack: A Library for Provenance-Tracking in Web-Based Visualizations}.  IEEE Visualization Conference (VIS), pp.\ 116-120, \doi{10.1109/VIS47514.2020.00030}, 2020. 
\item \uline{Jen Rogers}, Nicholas Spina, Ashley Neese, Rachel Hess, Darrel Brodke, \textbf{Alexander Lex}. \textit{Composer: Visual Cohort Analysis of Patient Outcomes}.  Workshop on Visual Analytics in Healthcare at AMIA (VAHC 2018), 2018. 
\item Thomas Geymayer, Manuela Waldner, \textbf{Alexander Lex}, Dieter Schmalstieg. \textit{How Sensemaking Tools Influence Display Space Usage}. The Eurographics Association EuroVis Workshop on Visual Analytics (EuroVA), \doi{10.2312/eurova.20171112}, 2017. 
\item Sean McKenna, \textbf{Alexander Lex}, Miriah Meyer. \textit{Worksheets for Guiding Novices through the Visualization Design Process}. IEEE Workshop on Pedagogy of Data Visualization (PDV), \doi{10.48550/arXiv.1709.05723}, 2017. 
\item \uline{Carolina Nobre}, \textbf{Alexander Lex}. \textit{OceanPaths: Visualizing Multivariate Oceanography Data}. The Eurographics Association Proceedings of the Eurographics Conference on Visualization (EuroVis) - Short Papers, \doi{10.2312/eurovisshort.20151124}, 2015. 
\item Manuela Waldner, \textbf{Alexander Lex}, Marc Streit, Dieter Schmalstieg. \textit{Design Considerations for Collaborative Information Workspaces in Multi-Display Environments}.  Proceedings of Workshop on Collaborative Visualization on Interactive Surfaces (CoVIS'09, VisWeek), pp.\ 36--39, 2009. 
\item Marc Streit, \textbf{Alexander Lex}, Heimo Müller, Dieter Schmalstieg. \textit{Gaze-Based Focus Adaption in an Information Visualization System}. IADIS Proceedings of the Conference on Computer Graphics and Visualization and Image Processing (CGVCVIP), 2009. 
